### 2022-04-01 manuscript.tex
april1st [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/0f21057cb2e3dcbcb14167218e80695a4c2cef5c.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/0f21057cb2e3dcbcb14167218e80695a4c2cef5c/checks
https://github.com/scherzerthesis/thesis/actions/runs/2078429685

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/ea3aab225306cad9bf38fdfcc0c9e01659bbf0fb/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/ea3aab225306cad9bf38fdfcc0c9e01659bbf0fb}{scherzerthesis/thesis@ea3aab2}
on April 1, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgfr1.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_1.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

@@

\#\#Conclusions
The broad purpose of this work was to better understand how BRAF\textsuperscript{V600E} tumors form and progress to lung adenocarcinoma.
Our strategy was (1) to determine additional tumor supressor genes in BRAF\textsuperscript{V600E} lung tumorigenesis, (2) evaluate effect different mutant-p53 alleles, and (3) profile the tumor cell heterogenity using scRNA-seq.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/0f21057cb2e3dcbcb14167218e80695a4c2cef5c/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/0f21057cb2e3dcbcb14167218e80695a4c2cef5c}{scherzerthesis/thesis@0f21057}
on April 1, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgfr_1.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgfr_2.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_1.png}
\caption{All lung cells collected from different genotypes.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_2.png}
\caption{Single cells broadly cluster into epithelial-, immune-, endothelial-, or mesenchymal- like cells.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_3.png}
\caption{Tumor cells cells are clustered based on treatment}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_4.png}
\caption{P53 transcriptional signature is identified in BRAV\textsuperscript{V600E}, p53-wildtype tumor cells}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/scrna_5.png}
\caption{Differentially expressed genes imparted by mutant-p53}\label{fig:04}
}
\end{figure}

@@

\hypertarget{preface}{%
\subsection{Preface}\label{preface}}

The broad purpose of this work was to better understand how BRAF\textsuperscript{V600E} tumors form and progress to lung adenocarcinoma.
Our strategy was (1) to determine additional tumor supressor genes in BRAF\textsuperscript{V600E} lung tumorigenesis, (2) evaluate effect different mutant-p53 alleles, and (3) profile the tumor cell heterogenity using scRNA-seq.
In this chapter, I will examine the exciting possibilities that arose as a consequence of my work. This will include a discussion on cooperating genetic events, p53 tumor supression, MAPK pathway targeted therapy, and tumor heterogenity.
